%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.05in,right=0.6in,bottom=0.5in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=red]{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% \name{debjit mandal} % Your name
% \address{\href{https://debjit-mandal.is-a.dev}{{https://debjit-mandal.is-a.dev}}} % Your address
% %\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
% \address{(+91) 8335024039 \\ debjitmandal8925@gmail.com} % Your phone number and email

\begin{document}
\begin{center}
{\Huge \bf DEBJIT MANDAL}\\ % Name in full capital letters and larger size
\vspace{0.2cm} % Maintain reduced vertical space between name and links
\begin{tabular}{ c c }
 \\ \faEnvelopeO\enspace debjitmandal8925@gmail.com & \faMobile\enspace (+91) 8335024039\\  
\end{tabular}
\vspace{0.1cm} % Slight reduction in space between the two rows
\begin{tabular}{ c c c }
 \faGlobe\enspace \href{https://debjit-mandal.is-a.dev}{debjit-mandal.is-a.dev} & \faGithub\enspace \href{https://github.com/debjit-mandal}{debjit-mandal} & \faLinkedin\enspace \href{https://linkedin.com/in/tensortrove}{tensortrove}\\  
\end{tabular}
\end{center}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Kalinga Institute of Industrial Technology, Bhubaneswar, Odisha} \hfill {\em 2022 - 2026} 
\\ B.Tech, Computer Science and Engineering \hfill {CGPA: 9.12}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}
%--copy and paste this region  if you need more--
\href{https://1drv.ms/i/s!AqmF3ryI8xyngdlvi5puoHlWRF5NTQ?e=hyfCRH}{{\bf CAMPUS AMBASSADOR}{, IMUNA}} \hfill {\em JULY, 2023- AUGUST, 2023}
\begin{itemize}
    \item Promoted IMUN Online Conferences in different schools/universities and got 10+ registrations.
    \item Best Intern for a week.
\end{itemize}
%--copy and paste this region  if you need more--
\end{rSection}
%--------------------------------------------------------------------------------
%    PROJECTS
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}

\begin{itemize}
       \item {\href{https://github.com/debjit-mandal/dsh}{{\bf DSH:}}
    Command-Line shell made using C++.
    \begin{itemize}
        \item Implemented custom command parsing for user-defined commands.
        \item Handled concurrency with multithreading for running background processes.
    \end{itemize}}
    
    \item{\href{https://github.com/debjit-mandal/Brain-Tumor-Detection}{{\bf Brain Tumor Detection:}} 
    A project that leverages deep learning techniques to automate the detection of brain tumors from MRI images.
    \begin{itemize}
        \item Utilized Convolutional Neural Networks (CNN) for image classification.
        \item Deployed the model using TensorFlow for real-time analysis.
    \end{itemize}}
    
    \item{\href{https://github.com/debjit-mandal/cifar10-resnet-classification}{{\bf CIFAR-10 ResNet Classification:}} 
    A project which focuses on classifying images from the CIFAR-10 dataset using a Residual Network (ResNet) architecture.
    \begin{itemize}
        \item Designed and trained a deep Residual Network (ResNet) model for image classification.
        \item Implemented data augmentation techniques to enhance model robustness.
    \end{itemize}}
    
    \item{\href{https://github.com/debjit-mandal/TrafficVisionAI}{{\bf TrafficVisionAI:}} 
    Real-Time Traffic Sign Recognition and Driver Assistance using AI.
    \begin{itemize}
        \item Integrated traffic sign recognition using TensorFlow and OpenCV.
        \item Developed lane detection and collision warning systems.
    \end{itemize}}
    
    \item{\href{https://github.com/debjit-mandal/MoodMelody}{{\bf MoodMelody:}} 
    Real-time emotion detection and content recommendation system.
    \begin{itemize}
        \item Implemented emotion recognition using TensorFlow/Keras.
        \item Integrated Spotify API for personalized music recommendations.
    \end{itemize}}
\end{itemize}
\end{rSection}

%--------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
\begin{itemize}
    \item {\bf Programming Languages:} Python, JAVA, C/C++, JavaScript, Rust, Go
    \item {\bf Web Technologies:} HTML, CSS, React.js, Node.js, Django
    \item {\bf Tools:} Git, Docker
    \item {\bf Frameworks \& Libraries:} TensorFlow, OpenCV, scikit-learn, Pandas, NumPy
    \item {\bf Databases:} SQLPlus, MongoDB
\end{itemize}
\end{rSection}
\end{document}----------------------------

